---
title: "Exercise A-2"
author: "Pablo Vidal Fernández"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
urlcolor: magenta
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F)
```

```{r, echo = F}
require(tidyverse)
require(knitr)
require(kableExtra)
require(xtable)
require(papeR)
```


**Exercise A.2.** For the [challenger.txt](https://www.youtube.com/watch?v=dQw4w9WgXcQ) dataset, do the following:

a.    Do a Poisson regression of the total number of incidents, *nfails.field* + *nfails.nozzle*, on *temp*.
Interpret the regression. Are the effects of temp significant with $\alpha = 0.01$?

We have to define our dependent variable as the sum of the two indicated variables. Then, we can do the regression:

```{r}
data <- read.table("challenger.txt", header = T)
data$total_fails <- data$nfails.field + data$nfails.nozzle
fit <- glm(total_fails ~ temp, family = poisson, data = data)
kable(prettify(summary(fit)))
```

The interpretations of the coefficients are the following:

-   $e^{\hat{\beta}_0} = e^{2.943} = 18.91$ is the expected number of total fails when *temp* is equal to 0.
-   $e^{\hat{\beta}_1} = e^{-0.143} = 0.866$ is the the factor by which the expected number of total fails is going to be decreased when there is an unit change in *temp* (13.4% reduction).

We can see that the effects of *temp* are significant with $\alpha = 0.01$, as the p-value is smaller and thus we can reject the null hypothesis of the coefficient being equal to 0.

b.    Plot the data and the fitted Poisson regression curve.

We create of sequence of 100 points evenly distributed between the minimum and the maximum observations of *temp*, and predict the expected number of total fails for each of them.

```{r}
x <- data$temp
y <- data$total_fails

plot(x, y, main = "Total fails vs temp", xlab = "Temp",
     ylab = "Total fails", pch = 16)

pred <- predict(fit, data.frame(temp = seq(min(x), max(x), 
                   length.out = 100)), type = "response")

lines(seq(min(x), max(x), length.out = 100), pred, col = 2, lwd = 2)
```

c.    Predict the expected number of incidents at temperatures -0.6 and 11.67.

The exercise asks for the expected number of incidents, so we will have to specify *type = response*. If we didn't specify it, the default argument *link* would give us $\hat{\eta}$, and we are interested in $e^{\hat{\eta}}$. 

```{r}
new_x <- data.frame(temp = c(-0.6, 11.67))
prediction <- predict(fit, new_x, type = "response")

df_pred <- cbind(new_x, prediction)
kable(df_pred)
```

We feel obligated to mention that the minimum observation for *temp* is 11.7 While the prediction for *temp* = 11.67 could be fine, as it is very close to observed data, we cannot be sure about the prediction for *temp* = -0.6. The model has not been trained on data with observations even near that temperature.